Required Libraries
```{r}
library(zoo)
library(xts)
library(quantmod)
library(forecast)
library(tseries)
library(readr)
library(dplyr)
library(extraDistr)
library(MASS)
library(triangle)
```

PART1
```{r, Part1}
# Define parameters
D <- 15000 # Annual demand
C <- 78 # Unit cost
H <- 0.18 # Holding cost rate (18%)
S <- 1180 # Ordering cost

# Define function to calculate annual ordering cost
annual_ordering_cost <- function(Q) {
  return((D * S) / Q)
}

# Define function to calculate annual holding cost
annual_holding_cost <- function(Q) {
  return((Q / 2) * C * H)
}

# Define function to calculate total annual inventory cost
total_inventory_cost <- function(Q) {
  return(annual_ordering_cost(Q) + annual_holding_cost(Q))
}

# Create a range of order quantities
order_quantities <- seq(100, 15000, by = 100)

# Calculate total cost for each order quantity
total_costs <- sapply(order_quantities, total_inventory_cost)

# Find the order quantity that minimizes total cost
optimal_quantity <- order_quantities[which.min(total_costs)]
min_cost <- min(total_costs)

# Plot Total Cost versus Order Quantity
plot(order_quantities, total_costs, type = "l", xlab = "Order Quantity", ylab = "Total Cost",
     main = "Total Cost vs. Order Quantity")
abline(v = optimal_quantity, col = "red")
text(optimal_quantity, min_cost, paste("Optimal Quantity:", optimal_quantity), pos = 4, col = "red")

# Print the optimal order quantity and corresponding total cost
cat("Optimal Order Quantity:", optimal_quantity, "\n")
cat("Minimum Total Cost:", min_cost, "\n")

```


Part 2
```{r, demandValues}
# Load the triangle package for the rtriangle function
library(triangle)

# Set the parameters
a <- 13000  # Minimum value
b <- 15000  # Mode
c <- 17000  # Maximum value

# Generate demand values
demand <- rtriangle(n = 1000, min<- a, max<- c, mode<- b)

# Check the generated demand values
print(demand)

```





```{r, Task2.1.1}
# Set the seed for reproducibility
set.seed(123)

# Define parameters
D <- 15000 # Annual demand
C <- 78    # Unit cost
H <- 0.18  # Holding cost rate (18%)
S <- 1180  # Ordering cost

# Define a function to calculate the annual ordering cost
annual_ordering_cost <- function(Q) {
  return((D * S) / Q)
}

# Define a function to calculate the annual holding cost
annual_holding_cost <- function(Q) {
  return((Q / 2) * C * H)
}

# Define a function to calculate the total annual inventory cost
total_inventory_cost <- function(Q) {
  return(annual_ordering_cost(Q) + annual_holding_cost(Q))
}

# Perform a simulation consisting of 1000 occurrences and calculate the minimum total cost for each occurrence
num_occurrences <- 1000
simulated_costs <- numeric(num_occurrences)

for (i in 1:num_occurrences) {
  # Generate a random demand from the triangular distribution
  demand <- rtriangle(n = 1, a <- 13000, b <- 15000, c <- 17000)
  
  # Calculate the order quantity using the EOQ formula
  order_quantity <- sqrt((2 * D * S) / (C * H))
  
  # Calculate the total cost
  total_cost <- total_inventory_cost(order_quantity)
  simulated_costs[i] <- total_cost
}

# (i) Estimate the expected minimum total cost by constructing a 95% confidence interval for it
expected_min_total_cost <- mean(simulated_costs)
# Compute mean and standard deviation of simulated costs
mean_simulated_costs <- mean(simulated_costs)
sd_simulated_costs <- sd(simulated_costs)

# Construct 95% confidence interval using mean and standard deviation
conf_interval_min_total_cost <- mean_simulated_costs + c(-1.96, 1.96) * (sd_simulated_costs / sqrt(num_occurrences))

# Print the results
cat("Expected Minimum Total Cost:", mean_simulated_costs, "\n")
cat("95% Confidence Interval for Minimum Total Cost:", conf_interval_min_total_cost[1], "-", conf_interval_min_total_cost[2], "\n")
# Plot histogram of simulated costs
# Increase the number of bins in the histogram
hist(simulated_costs, breaks = 50, freq = FALSE, main = "Histogram of Simulated Costs", xlab = "Total Cost")

# Overlay PDFs of various distributions
curve(dnorm(x, mean = mean_simulated_costs, sd = sd_simulated_costs), add = TRUE, col = "blue", lwd = 2, 
      ylab = "Density", xlab = "Total Cost", legend = "Normal")

# Add other PDFs for comparison (e.g., log-normal, gamma, etc.)
# curve(dlnorm(x, meanlog = meanlog, sdlog = sdlog), add = TRUE, col = "red", lwd = 2)
# curve(dgamma(x, shape, scale), add = TRUE, col = "green", lwd = 2)
# Add more curves for other distributions as needed

# Add legend
legend("topright", legend = c("Normal"), col = c("blue"), lwd = 2)

```

```{r,  2.1.2}
# Load the triangle package for the rtriangle function
library(triangle)

# Set the seed for reproducibility
set.seed(123)

# Define parameters
a <- 13000  # Minimum value
b <- 15000  # Mode
c <- 17000  # Maximum value
D <- 15000  # Annual demand
C <- 78     # Unit cost
H <- 0.18   # Holding cost rate (18%)
S <- 1180   # Ordering cost

# Define a function to calculate the annual ordering cost
annual_ordering_cost <- function(Q) {
  return((D * S) / Q)
}

# Define a function to calculate the annual holding cost
annual_holding_cost <- function(Q) {
  return((Q / 2) * C * H)
}

# Define a function to calculate the total annual inventory cost
total_inventory_cost <- function(Q) {
  return(annual_ordering_cost(Q) + annual_holding_cost(Q))
}

# Perform a simulation consisting of 1000 occurrences and calculate the order quantity for each occurrence
num_occurrences <- 1000
order_quantities <- numeric(num_occurrences)

for (i in 1:num_occurrences) {
  # Generate a random demand from the triangular distribution
  demand <- rtriangle(n = 1, a,  c,  b)
  
  # Calculate the order quantity using the EOQ formula
  order_quantity <- sqrt((2 * D * S) / (C * H))
  
  # Store the order quantity
  order_quantities[i] <- order_quantity
}
# Estimate the expected order quantity and construct a 95% confidence interval for it
mean_order_quantity <- mean(order_quantities)
sd_order_quantity <- sd(order_quantities)
conf_interval_order_quantity <- mean_order_quantity + c(-1.96, 1.96) * (sd_order_quantity / sqrt(num_occurrences))

# Print the results
cat("Expected Order Quantity:", mean_order_quantity, "\n")
cat("95% Confidence Interval for Order Quantity:", conf_interval_order_quantity[1], "-", conf_interval_order_quantity[2], "\n")
# Plot histogram of order quantities
hist(order_quantities, breaks = 20, freq = FALSE, main = "Histogram of Order Quantities", xlab = "Order Quantity")

# Overlay PDFs of various distributions for comparison
# For example, you can overlay normal, log-normal, and gamma distributions
curve(dnorm(x, mean = mean_order_quantity, sd = sd_order_quantity), add = TRUE, col = "blue", lwd = 2, 
      ylab = "Density", xlab = "Order Quantity", legend = "Normal")

# Add other PDFs for comparison (e.g., log-normal, gamma, etc.)
# curve(dlnorm(x, meanlog = meanlog, sdlog = sdlog), add = TRUE, col = "red", lwd = 2)
# curve(dgamma(x, shape, scale), add = TRUE, col = "green", lwd = 2)
# Add more curves for other distributions as needed

# Add legend

```

```{r,2.1.3, warning=FALSE}
# Sample data (replace this with your actual data)
orders <- c(10, 15, 20, 25, 30, 35, 40, 45, 50, 55)

# Step 1: Estimate the Expected Annual Number of Orders
mean_orders <- mean(orders)
std_dev_orders <- sd(orders)
n <- length(orders)
SE <- std_dev_orders / sqrt(n)
z <- qnorm(0.975)  # 95% confidence level, two-tailed
ME <- z * SE
lower_bound <- mean_orders - ME
upper_bound <- mean_orders + ME

cat("Estimated expected annual number of orders:", mean_orders, "\n")
cat("95% Confidence Interval:", lower_bound, "-", upper_bound, "\n")

# Step 2: Determine the Best-Fitting Probability Distribution
# Fit various distributions and compare their goodness of fit
# For example, you can try normal, Poisson, or exponential distributions

# Normal distribution
fit_normal <- fitdistr(orders, "normal")
cat("Parameters of the Normal distribution:", fit_normal$estimate, "\n")
hist(orders, freq = FALSE, main = "Histogram of Orders", xlab = "Number of Orders")
curve(dnorm(x, mean = fit_normal$estimate[1], sd = fit_normal$estimate[2]), 
      col = "blue", add = TRUE, lwd = 2)

# Poisson distribution
fit_poisson <- fitdistr(orders, "Poisson")
cat("Parameter of the Poisson distribution:", fit_poisson$estimate, "\n")
curve(dpois(x, lambda = fit_poisson$estimate), col = "red", add = TRUE, lwd = 2)

# Exponential distribution
fit_exponential <- fitdistr(orders, "exponential")
cat("Parameter of the Exponential distribution:", fit_exponential$estimate, "\n")
curve(dexp(x, rate = fit_exponential$estimate), col = "green", add = TRUE, lwd = 2)

# Step 3: Verify the Validity of the Chosen Distribution
# Visual inspection and statistical tests (e.g., chi-square goodness-of-fit test)
# Based on the observed data and the fitted distributions, assess the goodness of fit

legend("topright", legend = c("Normal", "Poisson", "Exponential"), col = c("blue", "red", "green"), lty = 1)



```

Observation:
32.5 orders per year are anticipated, with a 95% confidence interval of roughly 23.11739 to 41.88261.

Furthermore, the following are the estimated parameters for each distribution:

Mean = 32.5, Standard Deviation = 14.36141 is the normal distribution.
Distribution of Poissons: Rate parameter lambda = 32.5
Distribution exponential: Parameter for rate = 0.03076923

Anticipated Annual Order Volume: It is projected that 32.5 orders will be placed annually. This acts as a central estimate for the typical annual number of orders anticipated.

Confidence Interval: There is a 95% confidence interval between 23.11739 and 41.88261 for the anticipated yearly number of orders. This interval gives us a range that, for the true population parameter (expected number of orders), we can be 95% confident in.

Normal Distribution Parameters: A mean of 32.5 and a standard deviation of 14.36141 are the estimated values for the normal distribution. The data in this distribution are assumed to follow a bell-shaped, symmetric curve.

Poisson Distribution Parameter: A rate parameter (lambda) of 32.5 is the parameter estimated for the Poisson distribution. When modeling the quantity of events that take place within a given period of time or space, the Poisson distribution is frequently employed.

Exponential Distribution Parameter: A rate parameter of roughly 0.03076923 is the parameter estimated for the exponential distribution. When modeling the amount of time until the next independent event in a series of independent events, the exponential distribution is frequently utilized.

These observations shed light on the data's estimated distributional properties and can be useful in determining which probability distribution is best for modeling.

